Using CGM to Predict CFRD in the Envision Cohort

### 2025-05-27 Christine Chan/EnVision CF/cfrd_roc.qmd
Envision CFRD all thresholds

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

>>>>

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```
